Working title: Ecological network control

### 2018-05-15 paper/manuscript.Rmd
Change type for control_type attribute for consistency

# format networks for plotting
formatted_en_structural <- en_structural %>%
  purrr::map(~ fancify_vertex_name(.)) %>%
  purrr::map(~ add_property(., element = "edge", attr_name = "color", 'TRUE ~ "black"')) %>%
  purrr::map(~ add_property(., element = "edge", attr_name = "lty", "type == 'a' ~ 1", "TRUE ~ 3")) %>%
  purrr::map(~ add_property(., element = "vertex", attr_name = "color", "type == 'a' ~ 'white'", "TRUE ~ 'white'")) %>%
  purrr::map(~ add_property(., element = "vertex", attr_name = "frame.color", "type == 'a' ~ 'black'", "TRUE ~ 'white'")) %>%
  purrr::map(~ add_property(., element = "vertex", attr_name = "shape", "type == 'a' ~ 'circle'", "TRUE ~ 'square'")) %>%
  purrr::map(~ add_property(., element = "vertex", attr_name = "size", "type == 'a' ~ 55", "TRUE ~ 45")) %>%
  purrr::map(~ add_property(., element = "vertex", attr_name = "label.cex", "TRUE ~ 1")) %>%
  purrr::map(~ add_property(., element = "vertex", attr_name = "label.color", "TRUE ~ 'black'"))
```

>>>>

# format networks for plotting
formatted_en_structural <- en_structural %>%
  purrr::map(~ fancify_vertex_name(.)) %>%
  purrr::map(~ add_property(., element = "edge", attr_name = "color", 'TRUE ~ "black"')) %>%
  purrr::map(~ add_property(., element = "edge", attr_name = "lty", "control_type == 'a' ~ 1", "TRUE ~ 3")) %>%
  purrr::map(~ add_property(., element = "vertex", attr_name = "color", "control_type == 'a' ~ 'white'", "TRUE ~ 'white'")) %>%
  purrr::map(~ add_property(., element = "vertex", attr_name = "frame.color", "control_type == 'a' ~ 'black'", "TRUE ~ 'white'")) %>%
  purrr::map(~ add_property(., element = "vertex", attr_name = "shape", "control_type == 'a' ~ 'circle'", "TRUE ~ 'square'")) %>%
  purrr::map(~ add_property(., element = "vertex", attr_name = "size", "control_type == 'a' ~ 55", "TRUE ~ 45")) %>%
  purrr::map(~ add_property(., element = "vertex", attr_name = "label.cex", "TRUE ~ 1")) %>%
  purrr::map(~ add_property(., element = "vertex", attr_name = "label.color", "TRUE ~ 'black'"))
```
